\documentclass{memoir}
\input{/Users/tan19/Dropbox/LaTeXMacros.tex}

\title{Probability}
\author{Xi Tan (tan19@purdue.edu)}
\date{\today}

\begin{document}
\maketitle
\tableofcontents

\newpage
\chapter*{Preface}
This booklet is divided into 7 Chapters. The first chapter introduces the definitions of basic concepts, such as event, sample space, and probability space. Followed in the next chapter, we will discuss the relationship between two or more events when they interplay with each other. The third chapter formally brings in random variables and vectors, as a basis to develop their quantitative measure and characteristic functions later in chapter four. Chapter five includes some well-known limit theorems, which is useful for asymptotic analysis. The last two chapters will discuss several selected topics in probability theory, and provide a summary of common distributions.

\newpage
\part{Elementary Theory of Probability}
\input{./Elementary_Theory_of_Probability/Combinatorial_Analysis.tex}
\input{./Elementary_Theory_of_Probability/Conditional_Probability.tex}
\input{./Elementary_Theory_of_Probability/Probaility_Space.tex}
\input{./Elementary_Theory_of_Probability/Random_Variables.tex}
\input{./Elementary_Theory_of_Probability/Useful_Distributions.tex}
\input{./Elementary_Theory_of_Probability/Quantitative_Measure_and_Characteristic_Functions.tex}
\input{./Elementary_Theory_of_Probability/Limit_Theorems.tex}
\input{./Elementary_Theory_of_Probability/Selected_Topics_of_Probability.tex}


\newpage
\part{Elementary Theory of Stochastic Processes}
\input{./Elementary_Theory_of_Stochastic_Processes/Introduction.tex}
\input{./Elementary_Theory_of_Stochastic_Processes/Markov_Chains.tex}
\input{./Elementary_Theory_of_Stochastic_Processes/Poisson_Processes.tex}
\input{./Elementary_Theory_of_Stochastic_Processes/Renewal_Theory.tex}   
\input{./Elementary_Theory_of_Stochastic_Processes/Selected_Topics_of_Stochastic_Processes.tex}

\newpage
\part{Measure-theoretical Probability}
\chapter{Introduction}
\section{Why Do We Need Rigorous Probability Theory?}
Let's recall the axioms from non-measure probability courses. We have a \emph{sample space} $\Omega$, the elements of which $w \in \Omega$ called \emph{outcomes}, and the subsets $E \subset \Omega$ called \emph{events}. \emph{Probability measure} is nothing but assigning probability $P(E)$ to each event $E \subset \Omega$, under the following constraints:
\begin{enumerate}
	\item $P(E) \in [0,1]$
	\item $P(\Omega) = 1$
	\item $P(\uplus_{i=1}^\infty E_i) = \sum_{i=1}^n P(E_i)$
\end{enumerate}
where in the last constraint, `$\uplus$' means the union of \emph{disjoint} sets.

One of the motivations\footnote{Add unification of discrete and continuous r.v's.} of developing measure-theoretical probability theory is triggered by the following question:

\vspace{2 mm}
\textbf{Q: \emph{How do we know the three listed axioms are consistent, in particular, the last constraint?}}
\vspace{0.5 mm}

Actually, the \emph{Banach-Tarski paradox} and the \emph{Vitali paradox} are such counter examples (TBA). We have two choices: either we could reject the \emph{axiom of choice}, which is one of the basic assumptions made in the two paradoxes; or we could claim there are some subsets $E \subset \Omega$ that is `non-measurable'. In this course, we take the second solution.

\section{Normal Numbers}
\deff{
	Every $X \in [0,1]$ has a binary decimal expansion $X = 0.d_1d_2d_3\cdots$ or $X = \sum_{k=1}^\infty d_k 2^{-k}$, $d_k \in \{0,1\}$. However, it is possible that $X$ may have two expansions, for example, $X=0.111\cdots = 0.1000\cdots$. We choose the expansion ending in all 1's to make it well-defined.
}

\deff{
	$X \in (0,1)$ is normal if $\lim\limits_{n \to \infty} \frac{1}{n} \sum_{k=1}^n d_k = \frac{1}{2}$.
}

\prop{
	If $X \sim U(0,1)$, then $P(X\mbox{ is normal}) = 1$.
}

\lem{
	Suppose that $X_1, X_2, \cdots$ are i.i.d $Ber(1/2)$. Then $X = \sum_{n=1}^\infty X_n 2^{-n}$ is uniform on $(0,1)$.
}
\prof{	
	We (only) need to show $P(X \in (a,b]) = b - a$.\\
	
	Case 1: $\exists k, s.t. (a,b] = ((k-1)2^{-n}, k2^n]$. Since $(k-1)2^{-n} = 0.d_1d_2 \cdots d_n000\cdots$,
	\begin{align}
		P(X \in ((k-1)2^{-n},k2^{-n}]) &= P(X_1=d_1,X_2=d_2,\cdots,X_n=d_n, X_i=1 for i > n) = 2^{-n} = b-a
	\end{align}

	Case 2: $(a,b] = (l2^{-n},k2^{-n}], l < k$.
	\begin{align}
		P(X \in (l2^{-n},k2^{-n}]) &= (k-l)2^{-n} = b- a
	\end{align}

	In general, if $a < b$, let $a_n, b_n \in 2^{-n}\Z$ be s.t. $a_n \le a < a_n + 2^{-n}, b_n - 2^{-n} \le b < b_n$, then
	\begin{align}
		P(X \in (a,b]) \le P(X \in (a_n,b_n]) = b_n - a_n
	\end{align}
	$b_n - a_n - 2^{-n+1} = P(X \in (a_n+2^{-n},b_n-2^{-n}) \le \epsilon$. Note, $b-a \le b_n - a_n \le b- a + 2^{-n+1}$.

	We need to show that $P(\lim\limits_{n \to \infty} \frac{1}{n} \sum_{k=1}^\infty = \frac{1}{2}) = 1$. This is the SLLN.
}

We know that $\{X \in (a,b]\}$ are events. Why is $\{X\mbox{ is normal}\}$ an event?
\begin{align}
	\{X\mbox{ is normal}\} = \left\{\lim\limits_{n \to \infty} \frac{1}{n} \sum_{k=1}^\infty = \frac{1}{2}\right\} = \bigcap_{l=1}^\infty \bigcup_{m=l}^\infty \bigcap_{n=m}^\infty \left\{\left\vert \frac{1}{n} \sum_{k=1}^\infty - \frac{1}{2} \right\vert < \frac{1}{l} \right\}
\end{align}
This is equivalent to $\forall \epsilon = \frac{1}{l} > 0, \exists m < \infty, s.t., |\frac{1}{n} \sum_{k=1}^\infty - \frac{1}{2}| < \epsilon, \forall n \ge m$.

\section{Formal Definition of Probability Space}
\deff{
	A collection $\FF$ of subsets of $\Omega$ is a $\sigma$-field (or algebra) if
	\begin{enumerate}
		\item $\FF$ is non-empty;
		\item If $A \subset \FF$, then $A^c \in \FF$ (closed under complement);
		\item If $\{A_i\}$ is a countable sequence of elements of $\FF$, then $\cup_i A_i \in \FF$ (closed under countable unions).
	\end{enumerate}	
}
Note, 1) $\Omega \in \FF, \emptyset \in \FF$ since $\Omega = A \cup A^c if A \in \FF$. $\emptyset = \Omega^c$. 2) $\FF$ is closed under countable intersections.

\deff{
	A \emph{measure space} is a pair $(\Omega, \FF)$ where $\FF$ is a $\sigma$-field of subsets of $\Omega$.
}

\deff{
	A non-negative measure $\mu$ on $(\Omega, \FF)$ is a function $\mu: \FF \to \bar \RR_+ = [0,\infty]$ s.t.
	\begin{enumerate}
		\item $\mu(\emptyset) = 0$;
		\item If $A_i$ is a sequence of disjoint sets in $\FF$, then $\mu(\uplus_{i=1}^\infty A_i) = \sum_{i=1}^\infty \mu(A_i)$.
	\end{enumerate}
}

\deff{
	A \emph{probability space} is a triple $(\Omega, \FF, P)$ where $(\Omega, \FF)$ is a measure space, and $P$ is a measure on $(\Omega, \FF)$ with $P(\Omega) = 1$.
}

\ex{
	$\FF = 2^{\Omega}$ (all subsets of $\Omega$). If $\Omega = \Z$, then usually, $\FF = 2^\Omega$ is the $\sigma$-field we use. If $\Omega=(0,1]$ or $\R$, then $\FF$ is usually too big.
}

\ex{
	Let $\AA \subset 2^\Omega$, then $\sigma(\AA)$ is the smallest $\sigma$-field containing $\AA$. If $\OO \subset \R$ is the collection of all open subsets of $\R$, then $\sigma(\OO) = \BB$ is called the \emph{Borel $\sigma$-field}.
}

\chapter{Lecture 5 (1/21/2015 Wednesday): }
(Today and Friday) in Appendix A.
\deff{
	A non-empty collection of subsets $\AA \subset 2^\Omega$ is called an algebra if
	\begin{enumerate}
		\item $A \in \AA$ then $A^c \in \AA$
		\item $A, B \in \AA$ then $A \cup B \in \AA$
		\item $A, B \in \AA$ then $A \cap B \in \AA$
	\end{enumerate}
}

\deff{
	$\mu: \AA \rightarrow [0,\infty]$ is a measure on the algebra $\AA$ if
	\begin{enumerate}
		\item $\mu(\emptyset) = 0$
		\item If $\uplus_{i=1}^\infty A_i \in \AA$ then $\mu(\uplus_{i=1}^\infty A_i) = \sum_{i=1}^\infty \mu(A_i)$
	\end{enumerate}
}

\deff{
	A measure $\mu$ is $\sigma$-finite (on an algebra or a $\sigma$-field) if $\exists$ a sequence $A_n \nearrow \Omega$ with $\mu(A_n) < \infty$ ($A_n \subset A_{n+1}$ and $\Omega = \cup_{i=1}^\infty A_n$)
}

\begin{thm}
	(Caratheodory Extension) Let $\mu$ be a $\sigma$-finite measure on an algebra $\AA$. Then $\mu$ has a unique extension to a measure on $(\Omega, \sigma(\AA))$.
\end{thm}

Note: Meausre on algebras also satisfy Themorem 1.1.1
\begin{enumerate}
	\item $A \subset B$ then $\mu(A) \le \mu(B)$
	\item $\mu(\cup_{i=1}^\infty A_i \le \sum_i \mu(A_i)$ if $\cup A_i \in \AA$
\end{enumerate}


\chapter{Probability Space and Measure}

\section{Algebra of Sets}

\subsubsection{Set Operations}
Given two sets $A, B \in \Omega$, there are four basic binary operations on sets:
\begin{enumerate}
	\item {\em{Union}}: $A \cup B = \{x: x \in A \mbox{ or } x \in B\}$
	\item {\em{Intersection}}: $A \cap B = \{x: x \in A \mbox{ and } x \in B\}$
	\item {\em{Set difference}}: $A \setminus B = \{x: x \in A \mbox{ and } x \notin B\}$
	\item {\em{Set complement}}: $A^c = \Omega \setminus A$
\end{enumerate}

Set complement is the ``strongest'' operation, because if a collection of sets $\AA$ is closed under complement, and if it is also closed under any one of the other three operations, $\AA$ is closed under the rest two. That is seen from,
\begin{align}
	\mbox{If closed under } union &
	\begin{cases}
		A \cap B = (A^c \cup B^c)^c\\
		A \setminus B = A \cap B^c = (A^c \cup B)^c
	\end{cases}	
	\\
	\mbox{If closed under } intersection &
	\begin{cases}
		A \cup B = (A^c \cap B^c)^c\\		
		A \setminus B = A \cap B^c
	\end{cases}
	\\
	\mbox{If closed under } difference &
	\begin{cases}
		A \cap B = A \setminus (A \setminus B)\\
		A \cup B = (A^c \cap B^c)^c = (A^c \setminus (A^c \setminus B^c))^c\\
	\end{cases}		
\end{align}

The difference operation is the second ``strongest'' operation, in that if a collection of sets $\AA$ is closed under difference, it is closed under intersection, that is seen from,
\begin{align}
	A \cap B = A \setminus (A \setminus B)
\end{align}

The third ``strongest'' operation is the union, which can not be implied from difference or intersection, or their combination.

The ``weakest'' operation is the intersection, which can be implied from the difference.

To summarize, the ``strongest'' pair would be the complement plus any one more, which implies everything else; the second ``strongest'' would be the difference plus the union, which implies the intersection but not the complement ($\Omega$ may not be in the collection). \smallmarginpar{\textdbend}

\subsubsection{Class of Set Collection}
\begin{deff}
	Given a set $\Omega$, a non-empty collection $\PP \subset 2^\Omega$ is called a {\em{$\pi$-system}} iff:
	
	\center{$\forall A, B \in \PP$, $A \cap B \in \PP$}
\end{deff}
Notice, this has the weakest requirement.

\begin{deff}
	Given a set $\Omega$, a non-empty collection $\QQ \subset 2^\Omega$ is called a {\em{semiring}} iff:
	
	\center{$\forall A, B \in \QQ \mbox{ and } A \supset B$}
	\center{$\exists C_k \subset \QQ, s.t., A \setminus B = \bigcup_{k=1}^n C_k$}
\end{deff}

\begin{deff}
	Given a set $\Omega$, a non-empty collection $\RR \subset 2^\Omega$ is called a {\em{ring}} iff:
	
	\center{$\forall A, B \in \RR$, $A \cup B \in \RR$ and $B \setminus A \in \RR$}
\end{deff}

There are two points need to mention: the empty set is in a ring, since $A \setminus A = \emptyset$; $\AA$ is also closed under intersection (the reverse need not be true).

\begin{deff}
	A {\em{ring}} $\AA$ is called an {\em{field}} iff $\Omega \in \AA$.
\end{deff}
So a field is closed under all {\em{finite}} combination of set operations.


\begin{deff}
	An {\em{field}} is called a {\em{$\sigma$-field}} if for any sequence ${A_n}$ of sets in $\AA$, $\cup_{n \ge 1} A_n \in \AA$.
\end{deff}

$\not \exists$

\chapter{Integration Theory}
\chapter{Random Variables}
\chapter{Law of Large Numbers}
\section{Types of Convergence}
\subsubsection{Convergence in Distribution}
\subsubsection{Convergence in Probability}
\subsubsection{Almost Surely Convergence}
\subsubsection{$L^p$ Convergence}

\section{Weak Law of Large Numbers (WLLN)}
\section{Strong Law of Large Numbers (SLLN)}

\chapter{Central Limit theorem}

\chapter{Some Tricks}
\section{Prove by Contraposition}

\section{Construct Finer Partition}
Given twofinite partitions $\{A_n\}$ and $\{B_m\}$, a finer partition can be constructed as
\begin{align*}
	(\cup_{i=1}^n A_i) \bigcap (\cup_{j=1}^m B_j) = \bigcup (\cap_{i=1}^n \cap_{j=1}^m A_i B_j)
\end{align*}

\section{Prove Equality}
To prove two numerical quantities are equal $X=Y$, often times we can do this by showing $X \le Y$ and $X \ge Y$. Similarly, to prove two sets are equal $E = F$, we can show $E \subset F$ and $E \subset F$.

\section{An Epsilon of Room}
If one has to show that $X \le Y$, try proving that $X \le Y + \epsilon, \forall \epsilon > 0$. This trick combines well with the ``Prove Equality'' trick.

In a similar spirit, if one needs to show that a quantity $X$ vanishes, try showing that $|X| \le \epsilon, \forall \epsilon > 0$.

If one wants to show that a sequence $x_n$ of real numbers converges to zero, try showing that $\limsup_{n \to \infty} |x_n| \le \epsilon, \forall \epsilon > 0$

{\textbf{One caveat:}} for finite $x$, and any $\epsilon > 0$, it is true that $x + \epsilon > x$ and $x - \epsilon < x$, but it is not true when $x$ is equal to $+\infty$ or $-\infty$. \smallmarginpar{\textdbend}


\section{Interpretations of Probability}
\subsection{Cox's theorem}
\subsection{Principle of Maximum Entropy}

\part{Measure-theoretical Stochastic Processes}

\part{Appendix}

\end{document} 






