\documentclass{book}
\input{../LaTeXMacros.tex}

\title{Quantitative Finance}
\author{Xi Tan (xtan3.1415926@gmail.com)}

\makeindex

\begin{document}

\maketitle
\tableofcontents
\input{../preface}
\addcontentsline{toc}{chapter}{Preface}

\part{Background}
\chapter{Economical Finance}
\section{Capital Market Overview}
\section{Trading and Exchanges}
\section{Macroeconomic Environment}
\section{Classic Finance Theory}
\subsection{Time Value of Money}
\subsection{Capital Asset Pricing Model (CAPM)}


\chapter{Mathematical Finance}
\section{Probability Theory}
\subsection{Probability Space}
\subsection{Information and $\sigma$-Algebra}
\subsection{Conditional Expectation}
\subsection{Martingales}
\subsection{Change of Measure and Girsanov's Theorem}

\section{Brownian Motion and Stochastic Calculus}
\subsection{Stochastic Processes}
\subsection{Brownian Motion}
\subsection{Geometric Brownian Motion}
\subsection{It\^o Integral and It\^o Process}
\subsection{Function of It\^o Processes and It\^o's Lemma}

\section{Stochastic Differential Equations}
\subsection{The Feynman--Kac Formula}
\subsection{Kolmogorov Forward and Backward Equations}
\subsection{Explicitly Solvable Stochastic Differential Equations}
\subsection{Backward Induction (BI)}

\section{Probability Distribution}
\subsection{Poisson Distribution}
\subsection{Gaussian Distribution}
\subsection{Lognormal Distribution}
\subsection{$\chi^2$ Distribution}


\chapter{Statistical Finance}
\section{Regression}
\section{Classification}
\section{Machine Learning}
\section{Monte Carlo Simulation Methods}
\section{Moment Matching Methods}
\section{Copula Methods}

\chapter{Computational Finance}
\section{Linear Algebra}
\section{Numerical Analysis}
\section{Interpolation Methods}
\section{Root-finding Methods}
\subsection{The Bisection Method}
\subsection{The Newton--Raphson Method}
\subsection{The Secant Method}
\section{Optimization Methods}
\subsection{Linear Optimization}
\subsection{Non-linear Optimization}
\section{Software Engineering}


\part{Pricing, Investment, and Risk Management}
\chapter{Financial Modeling}
\section{Overview of (Arbitrage) Pricing Strategies}
\section{The Black--Scholes Model and Its Variants}
\subsection{The Black--Scholes Model}
\subsection{The Back--Scholes Model with Constant Dividend Yield (BS-D)}
\subsection{The Black's Model}
\section{Forward Models}
\subsection{Funding Spread Models}
\subsection{Dividend Models}
\section{Short Rate Models}
\subsection{Overview}
\subsection{Ornstein--Uhlenbeck Process}
\subsection{Square-root Process}
\section{Volatility Models}
\subsection{Implied Volatility Surface}
\subsection{Local Volatility Model}
\subsection{Stochastic Volatility Models}
\section{Jump Models}



\chapter{Investment Management}
\section{Asset Classes}
\subsection{Fixed Income}
\subsection{Equities}
\subsection{Foreign Exchange}
\subsection{Credit Derivatives}
\subsection{Interest Rate Derivatives}

\chapter{Risk Management}
\section{Risk Management Overview}
\subsection{Short-term Risk Management: Politics, Macroeconomics, Fundamental Analysis}
\subsection{Mid-term Risk Management: Technical Analysis, Sensitivity Analysis}
\subsection{Short-term Risk Management}

\section{Option Greeks}
\subsection{Delta}
\index{Delta}
\subsection{Gamma}
\index{Gamma}
\subsection{Vega}
\index{Vega}
\subsection{Theta}
\index{Theta}
\subsection{Hedging}

\section{Correlation and Skew}
\subsection{Implied Volatility Surface}
\subsection{Correlation}
\subsection{Skew}

\section{Term Structure, Duration, and Convexity}
\subsection{Term Structure of Interest Rate}
\subsection{Duration}
\subsection{Convexity}

\part{Miscellaneous}
\chapter{Study Notes}



\begin{thebibliography}{100} % 100 is a random guess of the total number of %references
\bibitem{Stewart} James Stewart {\em{Calsulus - Early Transcendentals}}. Cengage Learning, 2012
\bibitem{Rudin} Walter Rudin {\em{Principles of Mathematical Analysis}}. McGraw-Hill Companies, Inc., 1976.
\bibitem{Royden} H. L. Royden {\em{Real Analysis}}. Pearson Eduction, Inc., 1988.
\bibitem{Kreyszig} Erwin Kreyszig {\em{Introductory Functional Analysis with Applications}}. Wiley, 1989.
\bibitem{Folland} Gerald B. Folland {\em{Real Analysis: Modern Techniques and Their Applications}}. Wiley, 1999.
\bibitem{Torchinsky} Alberto Torchinsky {\em{Real Variables}}. Westview Press, 1995.

\bibitem{Wasserman} {\url{http://normaldeviate.wordpress.com/2012/11/17/what-is-bayesianfrequentist-inference/}}
\bibitem{Hochster} {\url{http://www.quora.com/What-is-the-difference-between-Bayesian-and-frequentist-statisticians}}
\bibitem{bayesian-inference advantage} {\url{http://www.bayesian-inference.com/advantagesbayesian}}
\bibitem{bayesian-inference likelihood} {\url{http://www.bayesian-inference.com/likelihood#likelihoodprinciple}}
\bibitem{Rossi} Rossi P, Allenby G, McCulloch R. {\emph{Bayesian Statistics and Marketing (pp. 4)}}. John Wiley \& Sons, 2005.
\bibitem{Efron 1978} Efron, Bradley. {\emph{Controversies in the Foundations of Statistics}}. The American Mathematical Monthly, Vol. 85, No. 4 (Apr., 1978), pp. 231-246.
\bibitem{Efron 2013} Efron, Bradley. {\emph{A 250-year Argument: Belief, Behavior, and the Bootstrap}}. Bull. Amer. Math. Soc. 50 (2013), 129-146.
\bibitem{quora CI} {\url{http://www.quora.com/Statistics-academic-discipline/What-is-a-confidence-interval-in-laymans-terms}}
\bibitem{quora diff} {\url{http://www.quora.com/What-is-the-difference-between-Bayesian-and-frequentist-statisticians}}
\bibitem{wiki} {\url{http://en.wikipedia.org/wiki/Confidence_interval#Meaning_and_interpretation}}

\bibitem{Minka} Thomas P. Minka. {\em{Old and New Matrix Algebra Useful for Statistics}}. December 28, 2000.
\bibitem{Wikepedia} \url{http://en.wikipedia.org/wiki/Matrix_calculus}. Accessed on \today
\bibitem{Searle} S. R. Searle and H. V. Henderson. {\em{A Primer on Differential Calculus for Vectors and Matrices}}. BU-1047-MB, 1993.
\bibitem{Nydick} Steven W. Nydick. {\em{A Different(ial) Way Matrix Derivatives Again}}. May 17, 2012.
\bibitem{Nydick} Steven W. Nydick. {\em{With(out) A Trace Matrix Derivatives the Easy Way}}. May 16, 2012.
\bibitem{Roweis} Sam Roweis. {\em{Matrix Identities}}. June 1999.
\bibitem{Tao} Terry Tao. {\em{Matrix identities as derivatives of determinant identities}}. January 13, 2013
\end{thebibliography}

\printindex

\end{document}
