%!TEX root = ../Probability.tex

\chapter{Introduction}
\deff{
	A \emph{stochastic process} is a collection of random variables $X(t)$ for $t \in T$, where the \emph{time} parameter $T$ is usually\footnote{It can be defined in a general space.} a subset of $\RR$. The set $\mathscr{S}$ containing all possible values of $X(t)$ is called the \emph{state space} of the process.
}

There are four common types of stochastic processes (with corresponding examples):
\begin{table}[h]
\centering
  \begin{tabular}{ | c | c | c | }
    \hline
     & \textbf{Finite or Countable State Space} & \textbf{Continuous State Space} \\ \hline
    \textbf{Discrete Time} & Markov Chains & Harris Chains \\ \hline
    \textbf{Continuous Time} & Poisson Processes and Hawkes Processes & Gaussian Processes and Wiener Processes \\ \hline    
  \end{tabular}
  \small{\caption{Four Common Types of Stochastic Processes.}}
\end{table}

\deff{
	A {\em{renewal process}} is an idealized stochastic model for events that occur randomly in time (generically called renewals or arrivals). The basic mathematical assumption is that the times between the successive arrivals are independent and identically distributed (i.i.d.). 
}

\deff{
	A {\em{delayed renewal process}} is just like an ordinary renewal process, except that the first arrival time is allowed to have a different distribution than the other inter-arrival times.
}


\deff{
	A {\em{counting process}} is a stochastic process $\{N(t), t \ge 0\}$ with values that are non-negative, integer, and increasing:
}

\deff{
	A {\em{point process}} is a collection of mathematical points randomly located on some underlying mathematical space such as the real line, the Cartesian plane, or more abstract spaces.
}

\deff{
	A {\em{diffusion process}} is a solution to a stochastic differential equation. For example, Brownian motion.
}

\deff{
	A {\em{jump process}} is a type of stochastic process that has discrete movements, called jumps, with random arrival times, rather than continuous movement, typically modeled as a simple or compound Poisson process.
}